%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Master's Degree in Mechanical Engineering (Field of Mechatronics and Robotics)} % Degree
  {Politecnico di Milano} % Institution
  {Milan, Lombardy, Italy} % Location
  {Sep. 2023 - PRESENT} % Date(s)
  {
    \begin{cvitems} % Description(s) bullet points
      \item {Joined the "Polimi Sailing Team" in the "Mechatronics" department}
    \end{cvitems}
  }

  %---------------------------------------------------------

  %---------------------------------------------------------
  \cventry
  {Master's Degree in Mechanical Engineering (Erasmus)} % Degree
  {University of Waterloo} % Institution
  {Waterloo, Ontario, Canada} % Location
  {Jan. 2024 - Apr. 2024} % Date(s)
  {
    Relevant courses taken:
    \vspace{4mm}
    \begin{cvitems} % Description(s) bullet points
      \item {Advanced Finite Element Analysis: coded a 2D FEM solver for non-linear and plastic materials in MATLAB}
      \item {Computational Fluid Dynamics: coded a 2D CFD solver for incompressible fluid in C and a 1D compressible fluid solver in MATLAB}
      \item {Materials for Nano and MEMS: complete a research project about Chip-Scale Atomic Clocks}
      % \item {Joined the "Waterloo Rocketry Team" in the "???" department}
    \end{cvitems}
  }

  %---------------------------------------------------------

  %---------------------------------------------------------
  \cventry
  {Bachelor's Degree in Mechanical Engineering} % Degree
  {Politecnico di Milano} % Institution
  {Milan, Lombardy, Italy} % Location
  {Sep. 2020 - Jul. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) bullet points
      \item {Selected for participating in the "Pro Hackin' Project 2023" (A.Y.2022/23)}
      \item {Selected for competing at SWERC 2021 (A.Y.2020/21)}
      \item {Third place in an internal coding competition using MATLAB (A.Y.2020/21)}
    \end{cvitems}
  }

  %---------------------------------------------------------

  %---------------------------------------------------------
  \cventry
  {High School Diploma, Scientific} % Degree
  {Scientific High School "Paolo Giovio"} % Institution
  {Como, Lombardy, Italy} % Location
  {Sep. 2015 - Jun. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) bullet points
      \item {Italian Physics Olympiad: admitted to regional selection (Feb. 2019)}
      \item {Italian Informatics Olympiad: admitted to regional selection (Apr. 2019, Apr. 2018)}
      \item {Italian Mathematics Olympiad: admitted to local district selection (Feb. 2017)}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
