%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  % %---------------------------------------------------------
  \cventry
  {Mechatronic Engineer} % Job title
  {Polimi Sailing Team} % Organization
  {Politecnico di Milano, Lombardy, Italy} % Location
  {Oct. 2023 - PRESENT} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Coded from scratch high performance NMEA0183 libraries.}
      \item {Worked with STM32 microcontrollers to create interfaces for the sensors and the control algorithms.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Mapper} % Job title
  {Orienteering Como} % Organization
  {Lombardy, Italy} % Location
  {May. 2018 - PRESENT} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Responsible for the society's cartography.}
      \item {Drawn several new Orienteering maps using the International Symbols Specification.}
      \item {Handled many homologation iter with the official Italian Federation for this sport.}
      \item {Developed a cloud-based architecture to facilitate the access and use of the map archive to all the members of the society.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software developer} % Job title
  {Confedilizia Como} % Organization
  {Como, Lombardy, Italy} % Location
  {Apr. 2020 - Feb. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Responsible for the development and distribution of a new software needed by the association.}
      \item {Developed the computer software for the specific needs and requests from the client.}
      \item {Developed the web platform (front-end \& database) for the secure distribution of the software to requesting clients.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Web Programmer} % Job title
  {Ennova Research} % Organization
  {Lomazzo, Lombardy, Italy} % Location
  {Jun. 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Period of internship for the "Alternanza Scuola Lavoro" national project.}
      \item {Developed a dynamically generated web page using Node.js and JavaScript.}
    \end{cvitems}
  }
\end{cventries}
