\descriptionstyle{
    \ifdefined\IsMechanical
        Mechanical engineer specialized in simulation-driven design, structural optimization, and rapid prototyping of complex systems.
        Experienced in translating physics and functional requirements into validated mechanical solutions through iterative CAD modeling (CATIA V5), FEM analysis (COMSOL, Altair HyperWorks, Ansys), and experimental testing.\\
        Strong background in multidisciplinary research environments with proven ability to move from simulation to hardware validation.
    \fi
    %
    \ifdefined\IsMechatronics
        Mechatronics Engineer with hands-on experience in modeling, control, and experimental validation of dynamic systems. \\
        Skilled in translating physics-based models into real-time control implementations, with a strong focus on rapid prototyping and iterative design.
        Strong analytical background in dynamics, control theory, and state estimation, complemented by CAD and FEM proficiency for mechanical design and optimization.
        Open to new challenges and eager to apply my multidisciplinary skill set to develop innovative solutions in R\&D environments.
    \fi
    %
    \ifdefined\IsSuperconductivity
        Aspiring superconductivity engineer with a strong foundation in physics and engineering principles. \\
        Currently expanding my knowledge in superconducting magnet technology for accelerator and detector applications, with a focus on understanding the underlying physics, materials science, and engineering challenges. \\
        Eager to apply my multidisciplinary background and hands-on engineering experience to contribute to the development of innovative superconducting solutions in research and industry.
    \fi
}